Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
better email addresses

            $^c$Open End, Göteborg, Sweden
           }
           {cfbolz@gmx.de, anto.cuni@gmail.com, fijal@merlinux.eu,
           leuschel@cs.uni-duesseldorf.de, samuele.pedroni@gmail.com, arigo@tunes.org}
%           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany} \and {merlinux GmbH, Hildesheim, Germany} \and {Open End, Göteborg, Sweden}

>>>>

            $^c$Open End, Göteborg, Sweden
           }
           {cfbolz@gmx.de \and anto.cuni@gmail.com \and fijal@merlinux.eu,
           leuschel@cs.uni-duesseldorf.de \and samuele.pedroni@gmail.com \and arigo@tunes.org}
